---
title: "crosstabs (> ^ , ^)>"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
header-includes:
- \usepackage{fancyhdr, xcolor}
- \pagestyle{fancy}
- \fancyhead[CO,CE]{}
- \fancyfoot[CO,CE]{\hyperlink{toc}{Back to TOC}}
- \fancyfoot[LE,RO]{\thepage}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE,fig.height=2.5)
source("libraries.R")
load(".RData")
my_report <- function(...) {

  fmt <- rmarkdown::pdf_document(...)

  fmt$knitr$knit_hooks$size = function(before, options, envir) {
    if (before) return(paste0("\n \\", options$size, "\n\n"))
    else return("\n\n \\normalsize \n")
  }

  return(fmt)
}

mnsd = function(x,y=NULL){
  
}
nmz = c("Total", ", male", ", female", ", educated", ", not educated")
```

```{r}
tmp = fbnum
a = tmp$q10.1_understand
af = a[tmp$q3.1_gender == "kvinde"]
am = a[tmp$q3.1_gender == "mand"]
aja = a[tmp$q5.1_digedu == "ja"]
anej = a[tmp$q5.1_digedu == "nej"]
#
b = rowMeans(tmp[,20:21])
b = round(b,1)
bf = b[tmp$q3.1_gender == "kvinde"]
bm = b[tmp$q3.1_gender == "mand"]
bja = b[tmp$q5.1_digedu == "ja"]
bnej = b[tmp$q5.1_digedu == "nej"]

#
c = rowMeans(tmp[,22:24])
c = round(c,1)
cf = c[tmp$q3.1_gender == "kvinde"]
cm = c[tmp$q3.1_gender == "mand"]
cja = c[tmp$q5.1_digedu == "ja"]
cnej = c[tmp$q5.1_digedu == "nej"]
```

# Definitions 

* \textbf{PK} (perceived knowledge) - q10 understand  with unique values `r sort(unique(a))`

* \textbf{TR} (trust) - "mean" of q15 trustsell and q16 trustpriv  with unique values `r sort(unique(b))`

* \textbf{ACP} (acceptance of commerical practices) - "mean" of q17 targetme, q18 targetfr and q19 comfortsell
with unique values `r sort(unique(c))`



Note that $\mu(1,3) = \mu(3,1) = \mu(2,2)$ etc... The table captions include $\chi^2$ test p-values, effect size estimates based on Cliff's $\delta$ as well as a t.test result for comparisson of the means "$\not =$" or "$=$".

* Large $\chi^2$ p-values indicate independence.

* Cliff's $\delta$ is an effect size measure for ordinal data $\in[-1,1]$ and is reported with 95% confidence intervals.

$$ \delta(x,y) < 0, \text{ for x "smaller" than y}$$
$$ \delta(x,y) > 0, \text{ for x "larger" than y}$$

In each section are shown three tables in the order PK vs TR, PK vs ACP and TR vs ACP. 

\newpage

# Facebook

`r paste(nmz, unlist(lapply(list(a,am,af,aja,anej),length)), collapse = "")`

## Plots

```{r, fig.height=6, fig.width=7}
par(mfrow=c(3,3),mar=c(4,4,2,.5))
barplot(table(a), col=grey.colors(1,.9,.3),ylab="Unconditional",xpd=NA)
fkit(a, col=1)
barplot(table(b), col=grey.colors(1,.9,.3))
fkit(b, col=1)
barplot(table(c), col=grey.colors(1,.9,.3))
fkit(c, col=1)

barplot(rbindme(am,af),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5), ylab="Gender")
fkit2(am, af, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(bm,bf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(bm, bf, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(cm,cf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(cm, cf, col=rainbow(2,start=.6,end=0,alpha = .5))
legend("right",c("M", "F"), fill=rainbow(2,start=.6,end=0,alpha = .5),bty="n",horiz=F,xpd=NA)

barplot(rbindme(aja,anej),beside=T,col=grey.colors(2,.7,.3), ylab="Dig. education", xlab = "PK")
fkit2(aja, anej, col=grey.colors(2,.7,.3))
barplot(rbindme(bja,bnej),beside=T,col=grey.colors(2,.7,.3), xlab = "TR")
fkit2(bja, bnej, col=grey.colors(2,.7,.3))
barplot(rbindme(cja,cnej),beside=T,col=grey.colors(2,.7,.3), xlab = "ACP")
fkit2(cja, cnej, col=grey.colors(2,.7,.3))
legend("right",c("Ja", "Nej"), fill=grey.colors(2,.7,.3),bty="n",horiz=F,xpd=NA)
```

## Summary table

```{r}
yet.another.table(chi=T)
# yet.another.table(chi=F)
```

\newpage


# Instagram

```{r}
tmp = ignum
a = tmp$q10.1_understand
af = a[tmp$q3.1_gender == "kvinde"]
am = a[tmp$q3.1_gender == "mand"]
aja = a[tmp$q5.1_digedu == "ja"]
anej = a[tmp$q5.1_digedu == "nej"]
#
b = rowMeans(tmp[,20:21])
b = round(b,1)
bf = b[tmp$q3.1_gender == "kvinde"]
bm = b[tmp$q3.1_gender == "mand"]
bja = b[tmp$q5.1_digedu == "ja"]
bnej = b[tmp$q5.1_digedu == "nej"]

#
c = rowMeans(tmp[,22:24])
c = round(c,1)
cf = c[tmp$q3.1_gender == "kvinde"]
cm = c[tmp$q3.1_gender == "mand"]
cja = c[tmp$q5.1_digedu == "ja"]
cnej = c[tmp$q5.1_digedu == "nej"]
```

`r paste(nmz, unlist(lapply(list(a,am,af,aja,anej),length)), collapse = "")`

## Plots

```{r, fig.height=6, fig.width=7}
par(mfrow=c(3,3),mar=c(4,4,2,.5))
barplot(table(a), col=grey.colors(1,.9,.3),ylab="Unconditional",xpd=NA)
fkit(a, col=1)
barplot(table(b), col=grey.colors(1,.9,.3))
fkit(b, col=1)
barplot(table(c), col=grey.colors(1,.9,.3))
fkit(c, col=1)

barplot(rbindme(am,af),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5), ylab="Gender")
fkit2(am, af, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(bm,bf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(bm, bf, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(cm,cf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(cm, cf, col=rainbow(2,start=.6,end=0,alpha = .5))
legend("right",c("M", "F"), fill=rainbow(2,start=.6,end=0,alpha = .5),bty="n",horiz=F,xpd=NA)

barplot(rbindme(aja,anej),beside=T,col=grey.colors(2,.7,.3), ylab="Dig. education", xlab = "PK")
fkit2(aja, anej, col=grey.colors(2,.7,.3))
barplot(rbindme(bja,bnej),beside=T,col=grey.colors(2,.7,.3), xlab = "TR")
fkit2(bja, bnej, col=grey.colors(2,.7,.3))
barplot(rbindme(cja,cnej),beside=T,col=grey.colors(2,.7,.3), xlab = "ACP")
fkit2(cja, cnej, col=grey.colors(2,.7,.3))
legend("right",c("Ja", "Nej"), fill=grey.colors(2,.7,.3),bty="n",horiz=F,xpd=NA)
```

## Summary table

```{r}
yet.another.table(chi=T)
# yet.another.table(chi=F)
```


\newpage

# Snapchat 

```{r}
tmp = scnum
a = tmp$q10.1_understand
af = a[tmp$q3.1_gender == "kvinde"]
am = a[tmp$q3.1_gender == "mand"]
aja = a[tmp$q5.1_digedu == "ja"]
anej = a[tmp$q5.1_digedu == "nej"]
#
b = rowMeans(tmp[,20:21])
b = round(b,1)
bf = b[tmp$q3.1_gender == "kvinde"]
bm = b[tmp$q3.1_gender == "mand"]
bja = b[tmp$q5.1_digedu == "ja"]
bnej = b[tmp$q5.1_digedu == "nej"]

#
c = rowMeans(tmp[,22:24])
c = round(c,1)
cf = c[tmp$q3.1_gender == "kvinde"]
cm = c[tmp$q3.1_gender == "mand"]
cja = c[tmp$q5.1_digedu == "ja"]
cnej = c[tmp$q5.1_digedu == "nej"]
```

`r paste(nmz, unlist(lapply(list(a,am,af,aja,anej),length)), collapse = "")`

## Plots

```{r, fig.height=6, fig.width=7}
par(mfrow=c(3,3),mar=c(4,4,2,.5))
barplot(table(a), col=grey.colors(1,.9,.3),ylab="Unconditional",xpd=NA)
fkit(a, col=1)
barplot(table(b), col=grey.colors(1,.9,.3))
fkit(b, col=1)
barplot(table(c), col=grey.colors(1,.9,.3))
fkit(c, col=1)

barplot(rbindme(am,af),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5), ylab="Gender")
fkit2(am, af, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(bm,bf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(bm, bf, col=rainbow(2,start=.6,end=0,alpha = .5))
barplot(rbindme(cm,cf),beside=T,col=rainbow(2,start=.6,end=0,alpha = .5))
fkit2(cm, cf, col=rainbow(2,start=.6,end=0,alpha = .5))
legend("right",c("M", "F"), fill=rainbow(2,start=.6,end=0,alpha = .5),bty="n",horiz=F,xpd=NA)

barplot(rbindme(aja,anej),beside=T,col=grey.colors(2,.7,.3), ylab="Dig. education", xlab = "PK")
fkit2(aja, anej, col=grey.colors(2,.7,.3))
barplot(rbindme(bja,bnej),beside=T,col=grey.colors(2,.7,.3), xlab = "TR")
fkit2(bja, bnej, col=grey.colors(2,.7,.3))
barplot(rbindme(cja,cnej),beside=T,col=grey.colors(2,.7,.3), xlab = "ACP")
fkit2(cja, cnej, col=grey.colors(2,.7,.3))
legend("right",c("Ja", "Nej"), fill=grey.colors(2,.7,.3),bty="n",horiz=F,xpd=NA)
```

## Summary table

```{r}
yet.another.table(chi=T)
# yet.another.table(chi=F)
```
