---
title: "notes"
output:
  word_document: default
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE)
source("main.R")
require(xtable)
require(knitr)
```

# Chisq p-values

- Null hypothesis  - independent
- Alternative hypothesis - they are NOT independent


* high p-value = there is no relation
* low p-value = there is a relation

Common treshold is 0.05 (or 5%) and I suggest you stick with it. So if a p-value is below 5% there is not enough evidence to support the null hypothesis that x and y are independent. You have to accept that x and y are dependent.

If the p-value is above 5% there is not enough evidence to disprove that x and y are independent. You have to accept that they are independent.

## H4

### H4a (table of counts)

The table of frequencies of use of different platforms. Based on the entire, combined, data set [Fb,Ig,Sc].

```{r}
x = rbind(table(dfo[,2]),table(dfo[,3]),table(dfo[,4]))
rownames(x) = names(dfo)[2:4]
kable(x)
```

### H4b (Chisq p-values)

Chisq tests of the type Platform_use_freq ~ q8.1, q8.2, q8.3. #PlatformSpecific, #BeforeAfter

```{r}
xfb1 = chisq.test(fbb$q1.1_usefb,fbb$q8.1_freqpost)$p.value
xfb2 = chisq.test(fbb$q1.1_usefb,fbb$q8.2_freqsend)$p.value
xfb3 = chisq.test(fbb$q1.1_usefb,fbb$q8.3_freqread)$p.value

yfb1 = chisq.test(fba$q1.1_usefb,fba$q8.1_freqpost)$p.value
yfb2 = chisq.test(fba$q1.1_usefb,fba$q8.2_freqsend)$p.value
yfb3 = chisq.test(fba$q1.1_usefb,fba$q8.3_freqread)$p.value

tbl1 = c(xfb1,xfb2,xfb3)
tbl1 = rbind(tbl1,c(yfb1,yfb2,yfb3))
colnames(tbl1) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

xig1 = chisq.test(igb$q1.2_useig,igb$q8.1_freqpost)$p.value
xig2 = chisq.test(igb$q1.2_useig,igb$q8.2_freqsend)$p.value
xig3 = chisq.test(igb$q1.2_useig,igb$q8.3_freqread)$p.value

yig1 = chisq.test(iga$q1.2_useig,iga$q8.1_freqpost)$p.value
yig2 = chisq.test(iga$q1.2_useig,iga$q8.2_freqsend)$p.value
yig3 = chisq.test(iga$q1.2_useig,iga$q8.3_freqread)$p.value

tbl2 = c(xig1,xig2,xig3)
tbl2 = rbind(tbl2,c(yig1,yig2,yig3))
colnames(tbl2) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl2) = c("noEdu","Edu")
kable(tbl2,digits=3,caption="Instagram")

xsc1 = chisq.test(scb$q1.3_usesc,scb$q8.1_freqpost)$p.value
xsc2 = chisq.test(scb$q1.3_usesc,scb$q8.2_freqsend)$p.value
xsc3 = chisq.test(scb$q1.3_usesc,scb$q8.3_freqread)$p.value

ysc1 = chisq.test(sca$q1.3_usesc,sca$q8.1_freqpost)$p.value
ysc2 = chisq.test(sca$q1.3_usesc,sca$q8.2_freqsend)$p.value
ysc3 = chisq.test(sca$q1.3_usesc,sca$q8.3_freqread)$p.value

tbl3 = c(xsc1,xsc2,xsc3)
tbl3 = rbind(tbl3,c(ysc1,ysc2,ysc3))
colnames(tbl3) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl3) = c("noEdu","Edu")
kable(tbl3,digits=3,caption="Snapchat")
```

---

---

## H5 (Chisq p-values)

Only fb_q9 and ig_q9 are answered correctly with disagreement. The rest of the questions sc_q9, 10, 11 and 12 for the three platforms are answered correctly with agreement.

```{r}
xfb1 = chisq.test(fbb$q9binary,fbb$q10binary)$p.value
xfb2 = chisq.test(fbb$q11binary,fbb$q12binary)$p.value

yfb1 = chisq.test(fba$q9binary,fba$q10binary)$p.value
yfb2 = chisq.test(fba$q11binary,fba$q12binary)$p.value

tbl1 = c(xfb1,xfb2)
tbl1 = rbind(tbl1,c(yfb1,yfb2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

xig1 = chisq.test(igb$q9binary,igb$q10binary)$p.value
xig2 = chisq.test(igb$q11binary,igb$q12binary)$p.value

yig1 = chisq.test(iga$q9binary,iga$q10binary)$p.value
yig2 = chisq.test(iga$q11binary,iga$q12binary)$p.value

tbl1 = c(xig1,xig2)
tbl1 = rbind(tbl1,c(yig1,yig2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Instagram")

xsc1 = chisq.test(scb$q9binary,scb$q10binary)$p.value
xsc2 = chisq.test(scb$q11binary,scb$q12binary)$p.value

ysc1 = chisq.test(sca$q9binary,sca$q10binary)$p.value
ysc2 = chisq.test(sca$q11binary,sca$q12binary)$p.value

tbl1 = c(xsc1,xsc2)
tbl1 = rbind(tbl1,c(ysc1,ysc2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Snapchat")

```

---

---

## H0

## H0a (Chisq p-values)

Caring about privacy settings vs eiditing privacy settings. Taken on the entire, combined, data set [fb,ig,sc]

```{r}
x = chisq.test(dfub$q2.1_nocare,dfub$q7.1_editedprivacy)$p.value
y = chisq.test(dfua$q2.1_nocare,dfua$q7.1_editedprivacy)$p.value
tbl = c("before"=x,"after"=y)
kable(tbl,digits=3)
```

### H0b (correlation)

```{r}
x = cor(dfonum$q2.1_nocare[dfonum$q5.1_digedu=="nej"],dfonum$q7.1_editedprivacy[dfonum$q5.1_digedu=="nej"])
y = cor(dfonum$q2.1_nocare[dfonum$q5.1_digedu=="ja"],dfonum$q7.1_editedprivacy[dfonum$q5.1_digedu=="ja"])
tbl = c("before"=round(x,3),"after"=round(y,3))
kable(tbl,digits=3)
```

---

---

## HX

### HXa (table of counts)

The row labels in the tables below are as well 1 to 4. Q15 vs Q16

```{r}
kable(table(fbb$q15.1_trustsell,fbb$q16.1_trustpriv),caption="Facebook before. q15 rows, q16 cols")
kable(table(fba$q15.1_trustsell,fba$q16.1_trustpriv),caption="Facebook after q15 rows, q16 cols")

kable(table(igb$q15.1_trustsell,igb$q16.1_trustpriv),caption="Instagram before. q15 rows, q16 cols")
kable(table(iga$q15.1_trustsell,iga$q16.1_trustpriv),caption="Instagram after q15 rows, q16 cols")

kable(table(scb$q15.1_trustsell,scb$q16.1_trustpriv),caption="Snapchat before. q15 rows, q16 cols")
kable(table(sca$q15.1_trustsell,sca$q16.1_trustpriv),caption="Snapchat after q15 rows, q16 cols")
```


### HXb (Chisq p-values)

Platform specific and before/after q15 vs q17, q18 and q19

```{r}
# Facebook
xfb1 = chisq.test(fbb$q15.1_trustsell,fbb$q17.1_targetme)$p.value
xfb2 = chisq.test(fbb$q15.1_trustsell,fbb$q18.1_targetfr)$p.value
xfb3 = chisq.test(fbb$q15.1_trustsell,fbb$q19.1_comfortsell)$p.value

yfb1 = chisq.test(fba$q15.1_trustsell,fba$q17.1_targetme)$p.value
yfb2 = chisq.test(fba$q15.1_trustsell,fba$q18.1_targetfr)$p.value
yfb3 = chisq.test(fba$q15.1_trustsell,fba$q19.1_comfortsell)$p.value

tbl1 = c(xfb1,xfb2,xfb3)
tbl1 = rbind(tbl1,c(yfb1,yfb2,yfb3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

# Instagram
xig1 = chisq.test(igb$q15.1_trustsell,igb$q17.1_targetme)$p.value
xig2 = chisq.test(igb$q15.1_trustsell,igb$q18.1_targetfr)$p.value
xig3 = chisq.test(igb$q15.1_trustsell,igb$q19.1_comfortsell)$p.value

yig1 = chisq.test(iga$q15.1_trustsell,iga$q17.1_targetme)$p.value
yig2 = chisq.test(iga$q15.1_trustsell,iga$q18.1_targetfr)$p.value
yig3 = chisq.test(iga$q15.1_trustsell,iga$q19.1_comfortsell)$p.value

tbl1 = c(xig1,xig2,xig3)
tbl1 = rbind(tbl1,c(yig1,yig2,yig3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Instagram")

# Snapchat
xsc1 = chisq.test(scb$q15.1_trustsell,scb$q17.1_targetme)$p.value
xsc2 = chisq.test(scb$q15.1_trustsell,scb$q18.1_targetfr)$p.value
xsc3 = chisq.test(scb$q15.1_trustsell,scb$q19.1_comfortsell)$p.value

ysc1 = chisq.test(sca$q15.1_trustsell,sca$q17.1_targetme)$p.value
ysc2 = chisq.test(sca$q15.1_trustsell,sca$q18.1_targetfr)$p.value
ysc3 = chisq.test(sca$q15.1_trustsell,sca$q19.1_comfortsell)$p.value

tbl1 = c(xsc1,xsc2,xsc3)
tbl1 = rbind(tbl1,c(ysc1,ysc2,ysc3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Snapchat")
```


