---
title: "notes"
output:
  pdf_document: default
  html_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE,fig.height=2.5)
source("main.R")
load(".RData")
require(xtable)
require(knitr)
```

# Summary

718 girls, 388 boys. Respondents fb 406, ig 192, sc 508. Had dig edu 298, had not eig edu 898.

```{r}
fx = lapply(fbb,table)
fy = lapply(fba,table)
fxb = lapply(fbb[fbb$q3.1_gender=="mand",],table)
fxg = lapply(fbb[fbb$q3.1_gender=="kvinde",],table)
fyb = lapply(fba[fba$q3.1_gender=="mand",],table)
fyg = lapply(fba[fba$q3.1_gender=="kvinde",],table)

ix = lapply(igb,table)
iy = lapply(iga,table)
ixb = lapply(igb[igb$q3.1_gender=="mand",],table)
ixg = lapply(igb[igb$q3.1_gender=="kvinde",],table)
iyb = lapply(iga[iga$q3.1_gender=="mand",],table)
iyg = lapply(iga[iga$q3.1_gender=="kvinde",],table)

sx = lapply(scb,table)
sy = lapply(sca,table)
sxb = lapply(scb[scb$q3.1_gender=="mand",],table)
sxg = lapply(scb[scb$q3.1_gender=="kvinde",],table)
syb = lapply(sca[sca$q3.1_gender=="mand",],table)
syg = lapply(sca[sca$q3.1_gender=="kvinde",],table)

print(str(dfo))
```

```{r}
x = dfo[dfo$q3.1_gender == "mand",]
y = dfo[dfo$q3.1_gender == "kvinde",]
par(mfrow=c(1,3))
barplot(rbind(table(x$q1.1_usefb),table(y$q1.1_usefb)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="fb")
barplot(rbind(table(x$q1.2_useig),table(y$q1.2_useig)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="ig")
barplot(rbind(table(x$q1.3_usesc),table(y$q1.3_usesc)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="sc")
```

```{r}
brief.plot.ol = function(what){
  par(mfrow=c(1,3))
  barplot(unlist(fx[what]),main=paste0("FB ",what))
  barplot(unlist(fy[what]),add=T)

  barplot(unlist(ix[what]),main=paste0("IG ",what))
  barplot(unlist(iy[what]),add=T)

  barplot(unlist(sx[what]),main=paste0("SC ",what))
  barplot(unlist(sy[what]),add=T)
}

brief.plot = function(what){
  par(mfrow=c(1,3),mar=c(4,2,4,1))
  barplot(rbind(unlist(fxb[what]),unlist(fxg[what])),beside=T,main=paste0("FB ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(fyb[what]),unlist(fyg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))

  barplot(rbind(unlist(ixb[what]),unlist(ixg[what])),beside=T,main=paste0("IG ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(iyb[what]),unlist(iyg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))
  
  barplot(rbind(unlist(sxb[what]),unlist(sxg[what])),beside=T,main=paste0("SC ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(syb[what]),unlist(syg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))
}
```

```{r}
brief.plot("q2.1_nocare")

```

```{r}
brief.plot("q6.1_school")
```

```{r}
brief.plot("q7.1_editedprivacy")
```

```{r}
brief.plot("q8.1_freqpost")
```

```{r}
brief.plot("q8.2_freqsend")
```

```{r}
brief.plot("q8.3_freqread")
```

```{r}
brief.plot("q9.1_seecontent")
```

```{r}
brief.plot("q10.1_understand")
```

```{r}
brief.plot("q11.1_seemypost")
```

```{r}
brief.plot("q12.1_controlseemypost")
```

```{r}
brief.plot("q13.1_audience")
```

```{r}
brief.plot("q14.1_trustconn")
```

```{r}
brief.plot("q15.1_trustsell")
```

```{r}
brief.plot("q16.1_trustpriv")
```

```{r}
brief.plot("q17.1_targetme")
```

```{r}
brief.plot("q18.1_targetfr")
```

```{r}
brief.plot("q19.1_comfortsell")
```

---

# Chisq p-values (Hypotheses for M and A)

- Null hypothesis  - independent
- Alternative hypothesis - they are NOT independent


* high p-value = there is no relation
* low p-value = there is a relation

Common treshold is 0.05 (or 5%) and I suggest you stick with it. So if a p-value is below 5% there is not enough evidence to support the null hypothesis that x and y are independent. You have to accept that x and y are dependent.

If the p-value is above 5% there is not enough evidence to disprove that x and y are independent. You have to accept that they are independent.

## H4

### H4a (table of counts)

The table of frequencies of use of different platforms. Based on the entire, combined, data set [Fb,Ig,Sc].

```{r}
x = rbind(table(dfo[,2]),table(dfo[,3]),table(dfo[,4]))
rownames(x) = names(dfo)[2:4]
kable(x)
```

### H4b (Chisq p-values)

Chisq tests of the type Platform_use_freq ~ q8.1, q8.2, q8.3. #PlatformSpecific, #BeforeAfter

```{r}
xfb1 = chisq.test(fbb$q1.1_usefb,fbb$q8.1_freqpost)$p.value
xfb2 = chisq.test(fbb$q1.1_usefb,fbb$q8.2_freqsend)$p.value
xfb3 = chisq.test(fbb$q1.1_usefb,fbb$q8.3_freqread)$p.value

yfb1 = chisq.test(fba$q1.1_usefb,fba$q8.1_freqpost)$p.value
yfb2 = chisq.test(fba$q1.1_usefb,fba$q8.2_freqsend)$p.value
yfb3 = chisq.test(fba$q1.1_usefb,fba$q8.3_freqread)$p.value

tbl1 = c(xfb1,xfb2,xfb3)
tbl1 = rbind(tbl1,c(yfb1,yfb2,yfb3))
colnames(tbl1) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

xig1 = chisq.test(igb$q1.2_useig,igb$q8.1_freqpost)$p.value
xig2 = chisq.test(igb$q1.2_useig,igb$q8.2_freqsend)$p.value
xig3 = chisq.test(igb$q1.2_useig,igb$q8.3_freqread)$p.value

yig1 = chisq.test(iga$q1.2_useig,iga$q8.1_freqpost)$p.value
yig2 = chisq.test(iga$q1.2_useig,iga$q8.2_freqsend)$p.value
yig3 = chisq.test(iga$q1.2_useig,iga$q8.3_freqread)$p.value

tbl2 = c(xig1,xig2,xig3)
tbl2 = rbind(tbl2,c(yig1,yig2,yig3))
colnames(tbl2) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl2) = c("noEdu","Edu")
kable(tbl2,digits=3,caption="Instagram")

xsc1 = chisq.test(scb$q1.3_usesc,scb$q8.1_freqpost)$p.value
xsc2 = chisq.test(scb$q1.3_usesc,scb$q8.2_freqsend)$p.value
xsc3 = chisq.test(scb$q1.3_usesc,scb$q8.3_freqread)$p.value

ysc1 = chisq.test(sca$q1.3_usesc,sca$q8.1_freqpost)$p.value
ysc2 = chisq.test(sca$q1.3_usesc,sca$q8.2_freqsend)$p.value
ysc3 = chisq.test(sca$q1.3_usesc,sca$q8.3_freqread)$p.value

tbl3 = c(xsc1,xsc2,xsc3)
tbl3 = rbind(tbl3,c(ysc1,ysc2,ysc3))
colnames(tbl3) = c("q8.1_freqpost","q8.2_freqsend","q8.3_freqread")
rownames(tbl3) = c("noEdu","Edu")
kable(tbl3,digits=3,caption="Snapchat")
```

---

---

## H5 (Chisq p-values)

Only fb_q9 and ig_q9 are answered correctly with disagreement. The rest of the questions sc_q9, 10, 11 and 12 for the three platforms are answered correctly with agreement.

```{r}
xfb1 = chisq.test(fbb$q9binary,fbb$q10binary)$p.value
xfb2 = chisq.test(fbb$q11binary,fbb$q12binary)$p.value

yfb1 = chisq.test(fba$q9binary,fba$q10binary)$p.value
yfb2 = chisq.test(fba$q11binary,fba$q12binary)$p.value

tbl1 = c(xfb1,xfb2)
tbl1 = rbind(tbl1,c(yfb1,yfb2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

xig1 = chisq.test(igb$q9binary,igb$q10binary)$p.value
xig2 = chisq.test(igb$q11binary,igb$q12binary)$p.value

yig1 = chisq.test(iga$q9binary,iga$q10binary)$p.value
yig2 = chisq.test(iga$q11binary,iga$q12binary)$p.value

tbl1 = c(xig1,xig2)
tbl1 = rbind(tbl1,c(yig1,yig2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Instagram")

xsc1 = chisq.test(scb$q9binary,scb$q10binary)$p.value
xsc2 = chisq.test(scb$q11binary,scb$q12binary)$p.value

ysc1 = chisq.test(sca$q9binary,sca$q10binary)$p.value
ysc2 = chisq.test(sca$q11binary,sca$q12binary)$p.value

tbl1 = c(xsc1,xsc2)
tbl1 = rbind(tbl1,c(ysc1,ysc2))
colnames(tbl1) = c("q9binary vs q10binary","q11binary vs q12binary")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Snapchat")

```

---

---

## H0

## H0a (Chisq p-values)

Caring about privacy settings vs eiditing privacy settings. Taken on the entire, combined, data set [fb,ig,sc]

```{r}
x = chisq.test(dfub$q2.1_nocare,dfub$q7.1_editedprivacy)$p.value
y = chisq.test(dfua$q2.1_nocare,dfua$q7.1_editedprivacy)$p.value
tbl = c("before"=x,"after"=y)
kable(tbl,digits=3)
```

### H0b (correlation)

```{r}
x = cor(dfonum$q2.1_nocare[dfonum$q5.1_digedu=="nej"],dfonum$q7.1_editedprivacy[dfonum$q5.1_digedu=="nej"])
y = cor(dfonum$q2.1_nocare[dfonum$q5.1_digedu=="ja"],dfonum$q7.1_editedprivacy[dfonum$q5.1_digedu=="ja"])
tbl = c("before"=round(x,3),"after"=round(y,3))
kable(tbl,digits=3)
```

---

---

## HX

### HXa (table of counts)

The row labels in the tables below are as well 1 to 4. Q15 vs Q16

```{r}
kable(table(fbb$q15.1_trustsell,fbb$q16.1_trustpriv),caption="Facebook before. q15 rows, q16 cols")
kable(table(fba$q15.1_trustsell,fba$q16.1_trustpriv),caption="Facebook after q15 rows, q16 cols")

kable(table(igb$q15.1_trustsell,igb$q16.1_trustpriv),caption="Instagram before. q15 rows, q16 cols")
kable(table(iga$q15.1_trustsell,iga$q16.1_trustpriv),caption="Instagram after q15 rows, q16 cols")

kable(table(scb$q15.1_trustsell,scb$q16.1_trustpriv),caption="Snapchat before. q15 rows, q16 cols")
kable(table(sca$q15.1_trustsell,sca$q16.1_trustpriv),caption="Snapchat after q15 rows, q16 cols")
```


### HXb (Chisq p-values)

Platform specific and before/after q15 vs q17, q18 and q19

```{r}
# Facebook
xfb1 = chisq.test(fbb$q15.1_trustsell,fbb$q17.1_targetme)$p.value
xfb2 = chisq.test(fbb$q15.1_trustsell,fbb$q18.1_targetfr)$p.value
xfb3 = chisq.test(fbb$q15.1_trustsell,fbb$q19.1_comfortsell)$p.value

yfb1 = chisq.test(fba$q15.1_trustsell,fba$q17.1_targetme)$p.value
yfb2 = chisq.test(fba$q15.1_trustsell,fba$q18.1_targetfr)$p.value
yfb3 = chisq.test(fba$q15.1_trustsell,fba$q19.1_comfortsell)$p.value

tbl1 = c(xfb1,xfb2,xfb3)
tbl1 = rbind(tbl1,c(yfb1,yfb2,yfb3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Facebook")

# Instagram
xig1 = chisq.test(igb$q15.1_trustsell,igb$q17.1_targetme)$p.value
xig2 = chisq.test(igb$q15.1_trustsell,igb$q18.1_targetfr)$p.value
xig3 = chisq.test(igb$q15.1_trustsell,igb$q19.1_comfortsell)$p.value

yig1 = chisq.test(iga$q15.1_trustsell,iga$q17.1_targetme)$p.value
yig2 = chisq.test(iga$q15.1_trustsell,iga$q18.1_targetfr)$p.value
yig3 = chisq.test(iga$q15.1_trustsell,iga$q19.1_comfortsell)$p.value

tbl1 = c(xig1,xig2,xig3)
tbl1 = rbind(tbl1,c(yig1,yig2,yig3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Instagram")

# Snapchat
xsc1 = chisq.test(scb$q15.1_trustsell,scb$q17.1_targetme)$p.value
xsc2 = chisq.test(scb$q15.1_trustsell,scb$q18.1_targetfr)$p.value
xsc3 = chisq.test(scb$q15.1_trustsell,scb$q19.1_comfortsell)$p.value

ysc1 = chisq.test(sca$q15.1_trustsell,sca$q17.1_targetme)$p.value
ysc2 = chisq.test(sca$q15.1_trustsell,sca$q18.1_targetfr)$p.value
ysc3 = chisq.test(sca$q15.1_trustsell,sca$q19.1_comfortsell)$p.value

tbl1 = c(xsc1,xsc2,xsc3)
tbl1 = rbind(tbl1,c(ysc1,ysc2,ysc3))
colnames(tbl1) = c("q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")
rownames(tbl1) = c("noEdu","Edu")
kable(tbl1,digits=3,caption="Snapchat")
```

## H6, Q13 vs Q14


```{r}
# Before
h6b1 = chisq.test(fbb$q13.1_audience,fbb$q14.1_trustconn)$p.value
h6b2 = chisq.test(igb$q13.1_audience,igb$q14.1_trustconn)$p.value
h6b3 = chisq.test(scb$q13.1_audience,scb$q14.1_trustconn)$p.value

# After 
h6a1 = chisq.test(fba$q13.1_audience,fba$q14.1_trustconn)$p.value
h6a2 = chisq.test(iga$q13.1_audience,iga$q14.1_trustconn)$p.value
h6a3 = chisq.test(sca$q13.1_audience,sca$q14.1_trustconn)$p.value

tbl = c(fb=h6b1,ig=h6b2,sc=h6b3)
tbl = rbind(tbl,c(fb=h6a1,ig=h6a2,sc=h6a3))
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits=3)
```


## H1, 10-05-2017, q15 vs q16

# Chisq

```{r}
x1 = chisq.test(fbb$q15.1_trustsell,fbb$q16.1_trustpriv)$p.value
x2 = chisq.test(igb$q15.1_trustsell,igb$q16.1_trustpriv)$p.value
x3 = chisq.test(scb$q15.1_trustsell,scb$q16.1_trustpriv)$p.value

y1 = chisq.test(fba$q15.1_trustsell,fba$q16.1_trustpriv)$p.value
y2 = chisq.test(iga$q15.1_trustsell,iga$q16.1_trustpriv)$p.value
y3 = chisq.test(sca$q15.1_trustsell,sca$q16.1_trustpriv)$p.value

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```

# Correlation

```{r}
x1 = cor(fbnumb$q15.1_trustsell,fbnumb$q16.1_trustpriv)
x2 = cor(ignumb$q15.1_trustsell,ignumb$q16.1_trustpriv)
x3 = cor(scnumb$q15.1_trustsell,scnumb$q16.1_trustpriv)

y1 = cor(fbnuma$q15.1_trustsell,fbnuma$q16.1_trustpriv)
y2 = cor(ignuma$q15.1_trustsell,ignuma$q16.1_trustpriv)
y3 = cor(scnuma$q15.1_trustsell,scnuma$q16.1_trustpriv)
tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```


## H2, 10-05-2017, q15 vs q17

# Chisq

```{r}
x1 = chisq.test(fbb$q15.1_trustsell,fbb$q17.1_targetme)$p.value
x2 = chisq.test(igb$q15.1_trustsell,igb$q17.1_targetme)$p.value
x3 = chisq.test(scb$q15.1_trustsell,scb$q17.1_targetme)$p.value

y1 = chisq.test(fba$q15.1_trustsell,fba$q17.1_targetme)$p.value
y2 = chisq.test(iga$q15.1_trustsell,iga$q17.1_targetme)$p.value
y3 = chisq.test(sca$q15.1_trustsell,sca$q17.1_targetme)$p.value

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```

# Correlation

```{r}
x1 = cor(fbnumb$q15.1_trustsell,fbnumb$q17.1_targetme)
x2 = cor(ignumb$q15.1_trustsell,ignumb$q17.1_targetme)
x3 = cor(scnumb$q15.1_trustsell,scnumb$q17.1_targetme)

y1 = cor(fbnuma$q15.1_trustsell,fbnuma$q17.1_targetme)
y2 = cor(ignuma$q15.1_trustsell,ignuma$q17.1_targetme)
y3 = cor(scnuma$q15.1_trustsell,scnuma$q17.1_targetme)

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```


## H3, 10-05-2017, q15 vs q18

# Chisq

```{r}
x1 = chisq.test(fbb$q15.1_trustsell,fbb$q18.1_targetfr)$p.value
x2 = chisq.test(igb$q15.1_trustsell,igb$q18.1_targetfr)$p.value
x3 = chisq.test(scb$q15.1_trustsell,scb$q18.1_targetfr)$p.value

y1 = chisq.test(fba$q15.1_trustsell,fba$q18.1_targetfr)$p.value
y2 = chisq.test(iga$q15.1_trustsell,iga$q18.1_targetfr)$p.value
y3 = chisq.test(sca$q15.1_trustsell,sca$q18.1_targetfr)$p.value

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```

# Correlation

```{r}
x1 = cor(fbnumb$q15.1_trustsell,fbnumb$q18.1_targetfr)
x2 = cor(ignumb$q15.1_trustsell,ignumb$q18.1_targetfr)
x3 = cor(scnumb$q15.1_trustsell,scnumb$q18.1_targetfr)

y1 = cor(fbnuma$q15.1_trustsell,fbnuma$q18.1_targetfr)
y2 = cor(ignuma$q15.1_trustsell,ignuma$q18.1_targetfr)
y3 = cor(scnuma$q15.1_trustsell,scnuma$q18.1_targetfr)

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```

## H4, 10-05-2017, q15 vs q19

# Chisq

```{r}
x1 = chisq.test(fbb$q15.1_trustsell,fbb$q19.1_comfortsell)$p.value
x2 = chisq.test(igb$q15.1_trustsell,igb$q19.1_comfortsell)$p.value
x3 = chisq.test(scb$q15.1_trustsell,scb$q19.1_comfortsell)$p.value

y1 = chisq.test(fba$q15.1_trustsell,fba$q19.1_comfortsell)$p.value
y2 = chisq.test(iga$q15.1_trustsell,iga$q19.1_comfortsell)$p.value
y3 = chisq.test(sca$q15.1_trustsell,sca$q19.1_comfortsell)$p.value

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```

# Correlation

```{r}
x1 = cor(fbnumb$q15.1_trustsell,fbnumb$q19.1_comfortsell)
x2 = cor(ignumb$q15.1_trustsell,ignumb$q19.1_comfortsell)
x3 = cor(scnumb$q15.1_trustsell,scnumb$q19.1_comfortsell)

y1 = cor(fbnuma$q15.1_trustsell,fbnuma$q19.1_comfortsell)
y2 = cor(ignuma$q15.1_trustsell,ignuma$q19.1_comfortsell)
y3 = cor(scnuma$q15.1_trustsell,scnuma$q19.1_comfortsell)

tbl = c(x1,x2,x3)
tbl = rbind(tbl,c(y1,y2,y3))
colnames(tbl) = c("fb","ig","sc")
rownames(tbl) = c("noEdu","Edu")
kable(tbl,digits = 3)
```