---
title: "notes"
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE,fig.height=2.5)
source("libraries.R")
load(".RData")
```



# Summary

718 girls, 388 boys. Respondents FB 406, IG 192, SC 508. Had digital education 298, did not have digital education 898. Q9 FB and IG have been inverted. All factor levels are of the form $1...n$ with 1 been disagreement and $n$ agreement. The Shinyapp needs a small fix to ensure better distribution of users between the three different surveys.

\pagebreak

# The data

```{r}
fx = lapply(fbb,table)
fy = lapply(fba,table)
fxb = lapply(fbb[fbb$q3.1_gender=="mand",],table)
fxg = lapply(fbb[fbb$q3.1_gender=="kvinde",],table)
fyb = lapply(fba[fba$q3.1_gender=="mand",],table)
fyg = lapply(fba[fba$q3.1_gender=="kvinde",],table)

ix = lapply(igb,table)
iy = lapply(iga,table)
ixb = lapply(igb[igb$q3.1_gender=="mand",],table)
ixg = lapply(igb[igb$q3.1_gender=="kvinde",],table)
iyb = lapply(iga[iga$q3.1_gender=="mand",],table)
iyg = lapply(iga[iga$q3.1_gender=="kvinde",],table)

sx = lapply(scb,table)
sy = lapply(sca,table)
sxb = lapply(scb[scb$q3.1_gender=="mand",],table)
sxg = lapply(scb[scb$q3.1_gender=="kvinde",],table)
syb = lapply(sca[sca$q3.1_gender=="mand",],table)
syg = lapply(sca[sca$q3.1_gender=="kvinde",],table)

print(str(dfu))
```

```{r}
x = dfo[dfo$q3.1_gender == "mand",]
y = dfo[dfo$q3.1_gender == "kvinde",]
par(mfrow=c(1,3))
barplot(rbind(table(x$q1.1_usefb),table(y$q1.1_usefb)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="fb")
barplot(rbind(table(x$q1.2_useig),table(y$q1.2_useig)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="ig")
barplot(rbind(table(x$q1.3_usesc),table(y$q1.3_usesc)),beside=T,col=rainbow(2,start=.55,end=0,alpha = .3),main="sc")
```

```{r}
brief.plot.ol = function(what){
  par(mfrow=c(1,3))
  barplot(unlist(fx[what]),main=paste0("FB ",what))
  barplot(unlist(fy[what]),add=T)

  barplot(unlist(ix[what]),main=paste0("IG ",what))
  barplot(unlist(iy[what]),add=T)

  barplot(unlist(sx[what]),main=paste0("SC ",what))
  barplot(unlist(sy[what]),add=T)
}

brief.plot = function(what){
  par(mfrow=c(1,3),mar=c(4,2,4,1))
  barplot(rbind(unlist(fxb[what]),unlist(fxg[what])),beside=T,main=paste0("FB ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(fyb[what]),unlist(fyg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))

  barplot(rbind(unlist(ixb[what]),unlist(ixg[what])),beside=T,main=paste0("IG ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(iyb[what]),unlist(iyg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))
  
  barplot(rbind(unlist(sxb[what]),unlist(sxg[what])),beside=T,main=paste0("SC ",what),
          col = rainbow(2,start=.55,end=0,alpha = .3),
          names.arg = 1:length(unlist(fxb[what])))
  barplot(rbind(unlist(syb[what]),unlist(syg[what])),beside=T,add=T,
          col = rainbow(2,start=.55,end=0,alpha = .7),
          names.arg = 1:length(unlist(fxb[what])))
}
```

```{r}
brief.plot("q2.1_nocare")

```

```{r}
brief.plot("q6.1_school")
```

```{r}
brief.plot("q7.1_editedprivacy")
```

```{r}
brief.plot("q8.1_freqpost")
```

```{r}
brief.plot("q8.2_freqsend")
```

```{r}
brief.plot("q8.3_freqread")
```

```{r}
brief.plot("q9.1_seecontent")
```

```{r}
brief.plot("q10.1_understand")
```

```{r}
brief.plot("q11.1_seemypost")
```

```{r}
brief.plot("q12.1_controlseemypost")
```

```{r}
brief.plot("q13.1_audience")
```

```{r}
brief.plot("q14.1_trustconn")
```

```{r}
brief.plot("q15.1_trustsell")
```

```{r}
brief.plot("q16.1_trustpriv")
```

```{r}
brief.plot("q17.1_targetme")
```

```{r}
brief.plot("q18.1_targetfr")
```

```{r}
brief.plot("q19.1_comfortsell")
```

\pagebreak


# L1. Concern, Q2 ~ Q7

Models with * did not converge properly. All models can potentially be improved significantly.

## Without demographic data

### Without interactions: Q7 ~ Q2 + digEdu + platform

```{r,results="asis"}
# my.barplot(luca1[[1]]$beta,namez = names(luca1[[1]]$beta),col=grey.colors(2,start=0,end=.4,alpha = .5))
# kable(sort(luca1[[1]]$beta, decreasing = T),digits = 2,caption="Coefficients")
notes.clm(luca1$q7.1_editedprivacy)
```

### With interactions: Q1 ~ (Q7 + DigEdu + platform)^2

```{r,results="asis"}
# my.barplot(luca1o2[[1]]$beta,namez = names(luca1o2[[1]]$beta),col=grey.colors(2,start=0,end=.4,alpha = .5))
# kable(sort(luca1o2[[1]]$beta, decreasing = T),digits = 2,caption="Coefficients")
notes.clm(luca2o2$q2.1_nocare)
```

## With demographic data

### Without interactions: Q2 ~ Q7 + DigEdu + paltform + demo.dat

```{r,results="asis"}
# my.barplot(luca2[[1]]$beta,namez = names(luca2[[1]]$beta),col=grey.colors(2,start=0,end=.4,alpha = .5))
# kable(sort(luca2[[1]]$beta, decreasing = T),digits = 2,caption="Coefficients")
notes.clm(luca3$q2.1_nocare)
```

### With interactions: Q7 ~ (Q1 + DigEdu + paltform + demo.dat)^2

```{r,results="asis"}
# my.barplot(luca2o2[[1]]$beta,namez = names(luca2o2[[1]]$beta),col=grey.colors(2,start=0,end=.4,alpha = .5))
# kable(sort(luca2o2[[1]]$beta, decreasing = T),digits = 2,caption="Coefficients")
notes.clm(luca4o2$q7.1_editedprivacy)
```



# L2. Knowledge?! 

Knowledge is defined as a factor whose levels are the combinations of the constituent questions (9-10, 11-12). For each pair of the questions 9,10 and 11-12 we create the derivative variables K1 and K2 such that for Q9 response i and Q10 response j the factor value of K1 is ij. K_1, K_2 have 16 elements each (4x4). In addition, based on the questions 9-19 we can build a wide range of derivative variables such as:

* knowledge (ignorance)
* awareness (naiveness)
* mindfulness (recklessness) etc

Below are tested the following 6 knowledge definitions:

* k1 = q9 & q10
* k2 = q11 & q 10
* k3 = q9 & q11
* k4 = q9 & q12
* k5 = q10 & q11
* k6 = q10 & q12


## Models for K1 and K2

### Without interactions: Q2, Q7 ~ K1 + digedu + platform

```{r,results="asis"}
# mluca1$q2.1_nocare$beta
# kable(sort(mluca1$q7.1_editedprivacy$beta,decreasing = T),digits = 2,caption = "Q7 Coefficients")
# lapply(mluca1,notes.clm)
# lapply(mluca1,notes.clm)
notes.clm(mluca1$q2.1_nocare)
notes.clm(mluca1$q7.1_editedprivacy)
```

### With interactions: Q2, Q7 ~ (K2 + digedu + platform)^2

```{r,results="asis"}
# cat("q2.1_nocare constant model\n")
# kable(sort(mluca2o2$q7.1_editedprivacy$beta,decreasing = T),digits = 2,caption = "Q7 Coefficients")
# lapply(mluca2o2,notes.clm)
notes.clm(mluca2o2$q2.1_nocare)
notes.clm(mluca2o2$q7.1_editedprivacy)
```

### Without interactions: Q2_, Q7_ ~ K1 + digedu + platform + demo.dat

```{r,results="asis"}
notes.clm(mluca4$q2.1_nocare)
notes.clm(mluca4$q7.1_editedprivacy)
```

## Models for K3 and K4

### With interactions: Q2, Q7 ~ (K3 + digedu + platform)^2

```{r,results="asis"}
# lapply(mluca6o2,notes.clm)
notes.clm(mluca6o2$q2.1_nocare)
notes.clm(mluca6o2$q7.1_editedprivacy)
```

### Without interactions: Q2, Q7 ~ K4 + digedu + paltform

```{r,results="asis"}
# lapply(mluca7,notes.clm)
notes.clm(mluca7$q2.1_nocare)
notes.clm(mluca7$q7.1_editedprivacy)
```

### With interactions: Q2_, Q7_ ~ (K3 + digedu + platform + demo.dat)^2

```{r,results="asis"}
# lapply(mluca8o2,notes.clm)
notes.clm(mluca8o2$q2.1_nocare)
notes.clm(mluca8o2$q7.1_editedprivacy)
```

### Without interactions: Q2_, Q7_ ~ K4 + digedu + platform + demo.dat

```{r,results="asis"}
# lapply(mluca9,notes.clm)
notes.clm(mluca9$q2.1_nocare)
notes.clm(mluca9$q7.1_editedprivacy)
```

## Models for K5 and K6

### With interactions: Q2, Q7 ~ (K5 + digedu + platform)^2

```{r,results="asis"}
# lapply(mluca10o2,notes.clm)
notes.clm(mluca10o2$q2.1_nocare)
notes.clm(mluca10o2$q7.1_editedprivacy)
```

### Without interactions: Q2, Q7 ~ K6 + digedu + platform

```{r,results="asis"}
# lapply(mluca11,notes.clm)
notes.clm(mluca11$q2.1_nocare)
notes.clm(mluca11$q7.1_editedprivacy)
```

### With interactions: Q2_, Q7_ ~ (K5 + digedu + platform + demo.dat)^2

```{r,results="asis"}
# lapply(mluca12o2,notes.clm)
notes.clm(mluca12o2$q2.1_nocare)
notes.clm(mluca12o2$q7.1_editedprivacy)
```

### Without interactions: Q2_, Q7_ ~ K6 + digedu + platform + demo.dat

```{r,results="asis"}
# lapply(mluca13,notes.clm)
notes.clm(mluca13$q2.1_nocare)
notes.clm(mluca13$q7.1_editedprivacy)
```
