---
title: "Report 1"
header-includes:
   - \usepackage{pdfpages}
output:
  pdf_document:
    toc: yes
    toc_depth: 3
    number_sections: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE,fig.height=2.5)
source("libraries.R")
library("knitr")
load(".RData")
```

\includepdf{Questions.pdf}

# Summary

All factor levels abbreviated wih 1...n should be read as "strongly disagree" ... "strongly agree". Removed 77 respondents which were assigned to surveys about platforms they dont use as indicated in Q1 use_platform. Removed 28 respondents which had no score above "4" (A few times per week) on questions 8.

Correlation between q2_nocare and q7_edit is -0.39 for those without digital education and -0.49 for those with digital education. Naive clustering (k-means) with 2 and 4 clusters did not show any relation to survey questions which is yet another indication that if any relations exist they are liekly to be conditional.

```{r}
tbl1 = table(dfu[,c("q3.1_gender","q5.1_digedu")])
tbl1 = rbind(tbl1,colSums(tbl1))
tbl1 = cbind(tbl1,rowSums(tbl1))
tbl1 = cbind(tbl1,tbl1[,1]/tbl1[,3])
rownames(tbl1)[3] = "total"
colnames(tbl1)[3:4] = c("total","percentage")
kable(tbl1,digits=2,caption="Digital education and gender")
```

```{r}
tbl2 = table(dfu[,c("q3.1_gender","q2.1_nocare")])
tbl2 = rbind(tbl2,colSums(tbl2))
tbl2 = cbind(tbl2,rowSums(tbl2))
tbl2 = cbind(tbl2,tbl2[,1:4]/tbl2[,5])
rownames(tbl2)[3] = "total"
colnames(tbl2)[5] = "total"
colnames(tbl2)[6:9] = paste0(1:4,"%")
kable(tbl2,digits=2,caption="NotCaring (q2) and gender")
```

```{r}
tbl3 = table(dfu[,c("q3.1_gender","bin_care")])
tbl3 = rbind(tbl3,colSums(tbl3))
tbl3 = cbind(tbl3,rowSums(tbl3))
tbl3 = cbind(tbl3,tbl3[,1]/tbl3[,3])
rownames(tbl3)[3] = "total"
colnames(tbl3)[3] = "total"
colnames(tbl3)[4] = "% agreeing"
kable(tbl3,digits=2,caption="BinaryNotCaring (q2) and gender")
```

```{r}
tbl4 = table(dfu[,c("platform","q2.1_nocare")])
tbl4 = rbind(tbl4,colSums(tbl4))
tbl4 = cbind(tbl4,rowSums(tbl4))
tbl4 = cbind(tbl4,tbl4[,1:4]/tbl4[,5])
rownames(tbl4)[4] = "total"
colnames(tbl4)[5] = "total"
colnames(tbl4)[6:9] = paste0(1:4,"%")
kable(tbl4,digits=2,caption="Platform and NotCaring (q2)")
```

```{r}
tbl5 = table(dfu[,c("platform","bin_care")])
tbl5 = rbind(tbl5,colSums(tbl5))
tbl5 = cbind(tbl5,rowSums(tbl5))
tbl5 = cbind(tbl5,tbl5[,1]/tbl5[,3])
rownames(tbl5)[4] = "total"
colnames(tbl5)[3] = "total"
colnames(tbl5)[4] = "% agreeing"
kable(tbl5,digits=2,caption="Platform and BinaryNotCaring (q2)")
```

```{r}
tbl6 = table(dfu[,c("q3.1_gender","platform")])
tbl6 = rbind(tbl6,colSums(tbl6))
tbl6 = cbind(tbl6,rowSums(tbl6))
tbl6 = cbind(tbl6,tbl6[,1:3]/tbl6[,4])
rownames(tbl6)[3] = "total"
colnames(tbl6)[4] = "total"
colnames(tbl6)[5:7] = paste0(1:3,"%")
kable(tbl6,digits=2,caption="Platform and gender")
```

# Histograms, means and st. deviations

Abbreviations:

\begin{itemize}
\item F - females
\item M - males
\item B - not having had digital education ("before")
\item A - having had digital education ("after")
\end{itemize}

The less saturated colors represent the participants which have not had digital education and v.v.

```{r}
fx = lapply(fbb,table)
fy = lapply(fba,table)
fxb = lapply(fbb[fbb$q3.1_gender=="mand",],table)
fxg = lapply(fbb[fbb$q3.1_gender=="kvinde",],table)
fyb = lapply(fba[fba$q3.1_gender=="mand",],table)
fyg = lapply(fba[fba$q3.1_gender=="kvinde",],table)

ix = lapply(igb,table)
iy = lapply(iga,table)
ixb = lapply(igb[igb$q3.1_gender=="mand",],table)
ixg = lapply(igb[igb$q3.1_gender=="kvinde",],table)
iyb = lapply(iga[iga$q3.1_gender=="mand",],table)
iyg = lapply(iga[iga$q3.1_gender=="kvinde",],table)

sx = lapply(scb,table)
sy = lapply(sca,table)
sxb = lapply(scb[scb$q3.1_gender=="mand",],table)
sxg = lapply(scb[scb$q3.1_gender=="kvinde",],table)
syb = lapply(sca[sca$q3.1_gender=="mand",],table)
syg = lapply(sca[sca$q3.1_gender=="kvinde",],table)
```


```{r,results='asis'}
for(i in names(dfnum)[sapply(dfnum,is.numeric)]){
  if(i == "q4.1_age") next # jump over age
  brief.plot(i)
  brief.table(i,caption=i)
  if(i > 3){
    brief.table.platform(i,caption=paste0(i, " per platform"))
  }
}
```

# PCA, FA and Chronbach's Alpha

Below are shown the Principal components, the unique variance, several factors and reduction according to Chronbach's alpha.

## Questions 9-12

```{r}
what = dfnum[,c("q9.1_seecontent","q10.1_understand","q11.1_seemypost","q12.1_controlseemypost")]
brief.pca(what,caption = "Questions 9-12")
```

## Questions 15-19

```{r}
what = dfnum[,c("q15.1_trustsell","q16.1_trustpriv","q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")]
brief.pca(what,factors=2,caption = "Questions 15-19")
```

## Questions 9-12, 15-19

```{r}
what = dfnum[,c("q9.1_seecontent","q10.1_understand","q11.1_seemypost","q12.1_controlseemypost",
                "q15.1_trustsell","q16.1_trustpriv","q17.1_targetme","q18.1_targetfr","q19.1_comfortsell")]
brief.pca(what,factors=3,check.keys=T,caption = "Questions 9-12, 15-19")
```

\newpage

# Models

With regards to modeling Q7 (I have edited my prvicay settings) there is a particular challange in that there are very few unique observations for which Q7 is 1 or 2. In other words, of all the possible combinations of Q2 (I don't care), gender and platform, only 1 combination, present only once in the data set, is unique for the values of Q7 == 1 and only one combination, present only once in the data set, is unique for Q7 == 2. 


```{r}
kable(a1[!apply(A1,1,any),],caption="Unique observations for Q7 = 1")
kable(a2[!apply(A2,1,any),],caption="Unique observations for Q7 = 2")
```

For the binary version of Q7 (with 0 meaning disagreement and 1 agreement) there are three unique combinations with a total of 5 observations. 

```{r}
kable(b1[!b12,],caption="Unique observations for binary Q7 = 0")
```
